Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
RGB giants @alex162 you're fired

A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}). Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H]. The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae. However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.

>>>>

A spectroscopic study of red giant branch (RGB) in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}). Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H]. The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae. However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.
